Visualization and analysis of probability distributions of large temporal data

### 2021-11-06 Rmd/00-c-declaration.Rmd
added declaration (need to run the percentages through Rob and Di)

`r if (knitr::is_html_output()) '<!--'`

@@

\begin{table}
\centering\footnotesize\tabcolsep=0.12cm
\begin{tabular}{|p{1cm}|p{2cm}|p{1.5cm}|p{3.5cm}|p{3.5cm}|p{1.5cm}|}
\hline
\RaggedRight\textbf{Thesis Chapter}  & \RaggedRight\textbf{Publication Title}  & \RaggedRight\textbf{Status (published, in press, accepted or returned for revision)}  & \RaggedRight\textbf{Nature and} {\%} \RaggedRight\textbf{of student contribution} & \RaggedRight\textbf{Co-author name(s) Nature and} {\%} \RaggedRight\textbf{of Co-author’s contribution} & \RaggedRight\textbf{Co-author(s), Monash student Y/N} \\ \hline
2 & Visualizing probability distributions across bivariate cyclic temporal granularities & Published & 70\%. Concept and developing software and writing first draft & (1) Rob J Hyndman, input into manuscript 15\% (2) Dianne Cook, Concept and input into manuscript 15\% & \multicolumn{1}{c|}{N} \\
\hline
3 & Detecting distributional differences between temporal granularities
for exploratory time series analysis & To be submitted & 80\%. Concept and developing software and writing first draft & (1) Rob J Hyndman, Concept and input into manuscript 10\% (2) Dianne Cook, Concept and input into manuscript 10\%  & \multicolumn{1}{c|}{N} \\
\hline
4 & Clustering time series based on probability distributions across temporal granularities & To be submitted & 70\%. Concept and developing software and writing first draft & (1) Dianne Cook, Concept and input into manuscript 20\% (2) Rob J Hyndman, concept and input into manuscript 10\% & \multicolumn{1}{c|}{N} \\
\hline
\end{tabular}
\end{table}

\FloatBarrier

>>>>

---
output:
  pdf_document: default
  html_document: default
---
`r if (knitr::is_html_output()) '<!--'`

@@

\begin{table}
\centering\footnotesize\tabcolsep=0.12cm
\begin{tabular}{|p{1cm}|p{2cm}|p{1.5cm}|p{3.5cm}|p{3.5cm}|p{1.5cm}|}
\hline
\RaggedRight\textbf{Thesis Chapter}  & \RaggedRight\textbf{Publication Title}  & \RaggedRight\textbf{Status (published, in press, accepted or returned for revision)}  & \RaggedRight\textbf{Nature and} {\%} \RaggedRight\textbf{of student contribution} & \RaggedRight\textbf{Co-author name(s) Nature and} {\%} \RaggedRight\textbf{of Co-author’s contribution} & \RaggedRight\textbf{Co-author(s), Monash student Y/N} \\ \hline
2 & Visualizing probability distributions across bivariate cyclic temporal granularities & Published & 70\%. Concept and developing software and writing first draft & (1) Rob J Hyndman, input into manuscript 15\% (2) Dianne Cook, Concept and input into manuscript 15\% & \multicolumn{1}{c|}{N} \\
\hline
3 & Detecting distributional differences between temporal granularities
for exploratory time series analysis & To be submitted & 70\%. Concept and developing software and writing first draft & (1) Rob J Hyndman, Concept and input into manuscript 15\% (2) Dianne Cook, Concept and input into manuscript 15\%  & \multicolumn{1}{c|}{N} \\
\hline
4 & Clustering time series based on probability distributions across temporal granularities & To be submitted & 70\%. Concept and developing software and writing first draft & (1) Dianne Cook, Concept and input into manuscript 20\% (2) Rob J Hyndman, concept and input into manuscript 10\% & \multicolumn{1}{c|}{N} \\
\hline
\end{tabular}
\end{table}
